Toxic Code Snippets on Stack Overflow

### 2017-11-13 cloverflow-tse/cloverflow.tex
Prepared for the photos and biographies.

% \begin{IEEEbiographynophoto}{Chaiyong Ragkhitwetsagul}
% Biography text here.
% \end{IEEEbiographynophoto}

% % if you will not have a photo at all:
% \begin{IEEEbiographynophoto}{Jens Krinke}
% Biography text here.
% \end{IEEEbiographynophoto}

% \begin{IEEEbiographynophoto}{Matheus Paixao}
% Biography text here.
% \end{IEEEbiographynophoto}

>>>>

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{cragkhit.jpg}}]{Chaiyong Ragkhitwetsagul}
is working toward the PhD degree in computer science at University College London, where he is part of the Centre for Research on Evolution, Search, and Testing (CREST) and Software Systems Engineering (SSE) Group. He is supervised by Jens Krinke and David Clark. His research interests include code search, code clone detection, software plagiarism, search-based software engineering, and mining software repository.
\end{IEEEbiography}
\vspace{-1cm}

% % if you will not have a photo at all:
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{jkrinke.jpg}}]{Jens Krinke}
is Senior Lecturer in the Software Systems Engineering
Group at the University College London, where he is Director of CREST,
the Centre for Research on Evolution, Search, and Testing.  His main
focus is software analysis for software engineering purposes. His
current research interests include software
similarity, modern code review, and mutation testing.  He is well known for his work on
program slicing and clone detection.
\end{IEEEbiography}
\vspace{-1cm}

\begin{IEEEbiography}{Matheus Paixao}
Biography text here.
\end{IEEEbiography}
\vspace{-1cm}

\begin{IEEEbiography}{Giuseppe Bianco}
	Biography text here.
\end{IEEEbiography}
\vspace{-0.5cm}

\begin{IEEEbiography}{Rocco Oliveto}
	Biography text here.
\end{IEEEbiography}
\vfill
